A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using SVD or High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
updates

\subsection{3-D Models and Simulations}\label{subsection:results_discussion_3d}

Following on from the work described for the 2-D models and simulations, Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a) and (b) presents the mesh grid for building the 3-D models. Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a), with 2109 tetrahedral elements, is the high resolution grid and is used to run the simulation for the 3-D base case. While Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(b), with 303 tetrahedral elements, is the low resolution grid used to run the simulation for the 3-D PCA(using HOSVD)-LinReg case. The number of tetrahedral elements for the low grid resolution grid is approximately $7$ times less than that for the high resolution grid.

>>>>

\subsection{3-D Models and Simulations}\label{subsection:results_discussion_3d}
Numerical simulations on 3D were also performed with the upscaled permeability distribution generated from the method described in Section~\ref{subsubsection:hosvdcase_preprocess_algorithm}. Figures~\ref{fig:HiRes_LowRes_3D_Mesh}a-b present the mesh grid used in the 3-D simulations. Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(a), with 2109 tetrahedral elements, is the high resolution grid and is used to run the simulation for the 3-D base case. While Figure~\ref{fig:HiRes_LowRes_3D_Mesh}(b), with 303 tetrahedral elements, is the low resolution grid used to run the simulation for the 3-D PCA(using HOSVD)-LinReg case. The number of tetrahedral elements for the low grid resolution grid is approximately $7$ times less than that for the high resolution grid.
